### 2013-09-18 chi2014/goals.tex
Goals: brainstorming metrices

>>>>

Researchers have used different metrices to assess the brainstorming process and its outputs. Typically, the measures of concern are the novelty of generated ideas, the practicality/appropriateness of ideas, the variety of ideas (flexibility), and quantity of ideas generated. \cite{finke1992creative, shah2003metrics}. The most common approach to measure novelty and appropriateness is to ask domain experts to subjectively make scale-rated assessment of each \cite{lewis2011affective, amabile_1983}. Depending on the types of artifacts and researchers' interest, these two measures are sometimes combined into one measure of quality \cite{little2010exploring}. Instead of subjective ratings, some researchers opt for a measure that can be derived objectively. For example, Jansson et al. used `o' scores, derived from the frequency an idea occur, to evaluate products novelty \cite{jansson_design_1991}. Flexibility is measured by the number of explored ``categories'' in a design space or by subjective rating from domain experts. \cite{lewis2011affective, marsh1996examples}. Category or feature-based quantities also yield other metrics such as within-catgories fluency and  the length of train-of-thought when participants focus on a particular category \cite{nijstad_how_2006}.

% Researchers have long debated how to best assess creativity in a way that consistently captures the complex dimensions of creativity [35]. The most commonly adopted approach [1, 5, 17] and the one we employ is to ask domain experts to subjectively make scale-rated assessments of creativity. Typically, domain experts rate originality, feasibility, elaboration, and flexibility and count the number of ideas generated [3].
